Corticosteroids for HELLP syndrome

### 2023-10-21 synthesis.Rmd
V1.2

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA)
knitr::opts_chunk$set(echo=FALSE)
knitr::opts_chunk$set(out.width = '110%')
library(meta)
library(readxl)
library(PRISMA2020)
library(knitr)
library(rsvg)
library(DiagrammeR)
library(tidyverse) 
library(DiagrammeRsvg)
library(htmlwidgets)
library(webshot)
```

@@

1.  Death
2.  Liver morbidity
3.  Pulmonary edema
4.  Renal failure
5.  Dialysis
6.  Platelet transfusion
7.  Perinatal death

## Death

@@

@@

## Pulmonary edema

@@

## Renal failure

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA)
knitr::opts_chunk$set(echo=FALSE)
knitr::opts_chunk$set(out.width = '110%')
library(meta)
library(readxl)
library(PRISMA2020)
library(knitr)
library(tidyverse)
library(robvis)
```

@@

1.  Maternal Death
2.  Liver morbidity (hematoma, rupture, failure)
3.  Acute pulmonary edema
4.  Acute renal failure
5.  Dialysis
6.  Platelet transfusion
7.  Perinatal death

## Maternal Death

@@

Risk of bias

```{r}
rob2md = read.csv("rob2md.csv") 
rob_summary(data = rob2md,tool = "ROB2")
rob_traffic_light(data = rob2md,tool = "ROB2")
```

@@

## Acute pulmonary edema

@@

## Acute renal failure
